```{r}
Howfarback <- 24000
Together <- matrix(nrow =1, ncol = 15)
colnames(Together) <- c("Points", "Price", "Designation", "Extra", "Winery", "Alcohol", "Size", "Category", "Date", "Title", "Review", "Name", "Country", "Region", "Subregion")
Thisrow <- matrix(nrow =1, ncol = 15)
colnames(Thisrow) <- c("Points", "Price", "Designation", "Extra", "Winery", "Alcohol", "Size", "Category", "Date", "Title", "Review", "Name", "Country", "Region", "Subregion")
start.time <- Sys.time()
Whichpage <- 1
Page <- 1
```
```{r}
for (i in 1:Howfarback){
  Page <- Page + 1
  if ((floor((i-1)/30) == (i-1)/30) && (i != 1)){
    Whichpage <- Whichpage + 10
      Page <- 2
  }
Deel1 <- "https://www.winemag.com/ratings/?s=&drink_type=wine&page="
Deel2 <- "&sort_by=pub_date_web&sort_dir=desc"
url1 <- paste(Deel1, Whichpage, Deel2, sep = "")

Yozes <- read_html(url1)
H1 <- "body > div.off-canvas-wrap > div > section > section > div.landing-page-reviews > section > div.row > div.large-9.column > div > div.results > ul > li:nth-child("
Yozes2 <- html_nodes(Yozes, paste(H1, Page, ") > a", sep= ""))
url <- html_attr(Yozes2, "href")

#Ding2 <- html_text(Ding1)
#Ding3 <- tolower(Ding2)
#Ding4 <- word(Ding3, 1:50)[which(!is.na(word(Ding3, 1:50)))]
#Ding4 <- gsub("[()]", "", Ding4)
#Ding5 <- paste(Ding4, sep="-", collapse=T)

webpage <- read_html(url)

Shizzle1 <- html_text(html_nodes(webpage,  '.medium-9 span , .medium-9 a , .primary-info .row:nth-child(2) .medium-9'))

Points <- html_text(html_nodes(webpage,  '#points'))[1]
Price <- html_text(html_nodes(webpage,  '.row:nth-child(1) .medium-9 span span'))
Designation <-html_text(html_nodes(webpage,  '.primary-info .row:nth-child(2) .medium-9 span span'))
if (length(Designation)==0){
  Designation <- "None"
}

Winery <- html_text(html_nodes(webpage,  '.row+ .row .medium-9 span span a'))
Alcohol <-  html_text(html_nodes(webpage,  '#review .row:nth-child(1) .small-9 span span'))
Category <- html_text(html_nodes(webpage,  '.secondary-info .row:nth-child(3) .small-9 span span'))

Info <- html_text(html_nodes(webpage,  '.small-9 > span span'))
Date <- Info[which(str_sub(Info, nchar(Info)-4, nchar(Info)-4)=="/")]
Size <- Info[which(grepl("ml", Info, ignore.case=T))]
if (length(Size)==0){
  Size <- ">1L"
}

Extra <- html_text(html_nodes(webpage, '#badges .badge'))
if (length(Extra)==0){
  Extra <- "None"
}

Title <- html_text(html_nodes(webpage, '.article-title'))
Review <- html_text(html_nodes(webpage, '.description'))
Name <- html_text(html_nodes(webpage, '#review .name'))
if (length(Name)==0){
  Name <- "Unknown"
}

Shizzle5 <- html_text(html_nodes(webpage, '.row:nth-child(4) a'))

Country <- Shizzle1[length(Shizzle1)-3]
Region <- Shizzle1[length(Shizzle1)-4]
Subregion <- Shizzle1[length(Shizzle1)-5]

Thisrow <- cbind(Points, Price, Designation, Extra, Winery, Alcohol, Size, Category, Date, Title, Review, Name, Country, Region, Subregion)

Together <- rbind(Together, Thisrow)
print(i)
}
